---
title: "ForageDB"
author: "Tania Barychka"
date: "19/11/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This is dedicated to explorative analysis of the FoRAGE dataset by Uiterwaal et al 2018 https://www.researchgate.net/publication/329938560_Data_paper_FoRAGE_Functional_Responses_from_Around_the_Globe_in_all_Ecosystems_database_a_compilation_of_functional_responses_for_consumers_and_parasitoids.

```{r echo=FALSE, warning=FALSE, message=FALSE}

library (ggplot2)
library(dplyr)          # for data manipulation
library(tidyr)          # for data shaping
library(ggpubr)
library(gridExtra)
```

Import data and summarise the explanatory variables.

```{r echo=FALSE}


#work
#forage_db<- read.csv("C:/Users/Tania Barychka/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")


#home
forage_db<- read.csv("C:/Users/Etherian/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")

#laptop
#forage_db<- read.csv("C:/Users/Tania/OneDrive/Documents/Madingley Postdoc/resource_map_doi_10_5063_F17H1GTQ/data/FoRAGE_db_12_19_18_data_set.csv")


head(forage_db)

forage_db<-forage_db[-c(2084:2682),]


summary(forage_db)
#head(forage_db)

#table(forage_db$Vert.invert)
#table(forage_db$Habitat)
table(forage_db$Vert.invert, forage_db$Major.grouping.1)

#ggplot(forage_db, aes(Vert.invert[forage_db$Vert.invert=="Vertebrate"], ))

```


Let's have a look at the data.

```{r echo=FALSE}

ggplot(forage_db, aes(Vert.invert))+geom_histogram(stat="count")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")

fit_bodyMass<-lm(log10(forage_db$Predator.mass..mg.)~log10(forage_db$Prey.mass..mg.))
summary(fit_bodyMass)

bm<-ggplot(forage_db, aes(log10(Prey.mass..mg.),log10(Predator.mass..mg.), col=Vert.invert))+geom_point()+geom_abline(slope =  0.74612, intercept =  1.74694,col="red")+ggtitle("Predator vs Prey Body mass")

bm+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+ylab("Log 10 Predator Mass, mg")+xlab("Log10 Prey mass, mg")

ggplot(forage_db, aes(Mean.R2.of.fits))+geom_histogram(stat="bin", binwidth = 0.05)+geom_vline(xintercept=mean(forage_db$Mean.R2.of.fits), col="red")+geom_vline(xintercept=median(forage_db$Mean.R2.of.fits), col="blue")+ggtitle("Mean R2 of bootstrapped fits")+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")


#Look at attck rate fits with body mass
aFits_PredBM<-ggplot(forage_db, aes(log10(Predator.mass..mg.),log10(Fitted.a..median.of.BS.samples.), col=Vert.invert))+geom_point()

aFits_PredBM+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+xlab("Log 10 Predator Mass, mg")+ylab("Log10 Fitted attack rate median of bootstapped samples")+ggtitle("Fitted attack rate values with Predator mass")

aFits_PreyBM<-ggplot(forage_db, aes(log10(Prey.mass..mg.),log10(Fitted.a..median.of.BS.samples.), col=Vert.invert))+geom_point()

aFits_PreyBM+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+xlab("Log 10 Prey Mass, mg")+ylab("Log10 Fitted attack rate median of bootstapped samples")+ggtitle("Fitted attack rate values with Prey mass")


#Look at handling time fits with body mass
hFits_PredBM<-ggplot(forage_db, aes(log10(Predator.mass..mg.),log10(Fittted.h..day.), col=Vert.invert))+geom_point()

hFits_PredBM+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+xlab("Log 10 Predator Mass, mg")+ylab("Log10 Fitted handling time")+ggtitle("Fitted handling time with Predator mass")

hFits_PreyBM<-ggplot(forage_db, aes(log10(Prey.mass..mg.),log10(Fittted.h..day.), col=Vert.invert))+geom_point()

hFits_PreyBM+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+xlab("Log 10 Prey Mass, mg")+ylab("Log10 Fitted handling time")+ggtitle("Fitted handling time with Prey mass")

which(forage_db$Vert.invert=="Angiosperm")

```

Data Exploration - 07/01/2020
--

Following Zuur, Ieno and Elphick (2010) in MEE.

X = Predator Body Mass; Prey Body Mass and Temperature
Y1: Attack Rates
Y2: Handling Time

1. Outliers in X and Y:
--

**1.1 Outliers in Response Variables: Attack Rates**

```{r echo=FALSE,fig.height=7, fig.width=10}

par(mfrow=c(1,2))
#Fitted Attack Rates
boxplot(forage_db$Fitted.a..median.of.BS.samples., ylab="Fitted attack rates")
dotchart(forage_db$Fitted.a..median.of.BS.samples., ylab="Order of the data")
par(mfrow=c(1,1))
ggplot(forage_db[forage_db$Vert.invert!="",],aes( Vert.invert, Fitted.a..median.of.BS.samples.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())


#ggplot(forage_db, aes(Fitted.a..median.of.BS.samples.))+geom_point()

which(forage_db$Fitted.a..median.of.BS.samples.>100000000)


```

There is one very serious outlier in the attack rates. This estimate of attack rate is based on raw data of lynx preying on roe deer.
Without the large outlier:

```{r echo=FALSE,fig.height=7, fig.width=10}

par(mfrow=c(1,2))
#Fitted Attack Rates
boxplot(forage_db$Fitted.a..median.of.BS.samples.[which(forage_db$Fitted.a..median.of.BS.samples.<1000000000)], ylab="Fitted attack rates", main ="Removed the largest outlier")
dotchart(forage_db$Fitted.a..median.of.BS.samples.[which(forage_db$Fitted.a..median.of.BS.samples.<1000000000)], ylab="Order of the data")


a1<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert!="Vertebrate" & forage_db$Vert.invert!="Invertebrate",],aes( Vert.invert, Fitted.a..median.of.BS.samples.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+ggtitle("Grouped:")+theme(axis.title.x=element_blank())

a2<- ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Vertebrate" | forage_db$Vert.invert=="Invertebrate",],aes( Vert.invert, Fitted.a..median.of.BS.samples.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

grid.arrange(a1,a2, ncol=2)

which(forage_db$Fitted.a..median.of.BS.samples.>3000  & forage_db$Vert.invert=="Invertebrate")
```

**1.2 Handling times**

```{r echo=FALSE,fig.height=7, fig.width=10}

#Fitted handling times
par(mfrow=c(1,2))
boxplot(forage_db$Fittted.h..day., ylab="Fitted handling times (day)")

dotchart(forage_db$Fittted.h..day., ylab="Order of the data")

ggplot(forage_db[forage_db$Vert.invert!="",],aes( Vert.invert,Fittted.h..day.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

```



```{r echo=FALSE, fig.height=7, fig.width=10}


h1<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert!="Vertebrate" & forage_db$Vert.invert!="Invertebrate",],aes( Vert.invert, Fittted.h..day.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+ggtitle("Grouped:")+theme(axis.title.x=element_blank())

h2<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Vertebrate" | forage_db$Vert.invert=="Invertebrate",],aes( Vert.invert, Fittted.h..day.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

grid.arrange(h1,h2, ncol=2)

```

Some large outliers, particularly  in **the vertebrates' handling times and attack rates**.

Zuur et al. (2010) recommends care when dealing with outliers in the response variable, especially when they represent genuine variation in the responses. Here, our responses are fitted attack rates of bootstrapped samples and fitted handling times. 

One option for dealing with outliers in the response is to transform. However, Zuur et al. recommends choosing a statistical method that uses a probability distribution that allows greater variation for larger mean values, e.g. gamma for continuous data and Poisson or negative binomial for count data.

**1.3 Outliers in Covariates: Predator** 



```{r echo=FALSE}

#Adult body masses
#Predator

#Fitted handling times
par(mfrow=c(1,2))
boxplot(forage_db$Predator.mass..mg., ylab="Predator mass (mg)")

dotchart(forage_db$Predator.mass..mg., ylab="Order of the data")

#ggplot(forage_db[forage_db$Vert.invert!="",],aes( Vert.invert,Predator.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
#panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")


```


```{r echo=FALSE, fig.height=7, fig.width=10}

predBM1<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Angiosperm",],aes( Vert.invert, Predator.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+ggtitle("Grouped:")+theme(axis.title.x=element_blank())



predBM2<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Protozoan",],aes( Vert.invert, Predator.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),axis.title.x=element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

predBM3<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Invertebrate",],aes( Vert.invert, Predator.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),axis.title.x=element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())
                                                                                                                                                                                                                                      
predBM4<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Vertebrate",],aes( Vert.invert, Predator.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),axis.title.x=element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

grid.arrange(predBM1,predBM2, predBM3,predBM4, ncol=2)

#THe largest outliers in vert
which(forage_db$Predator.mass..mg.>100000000  & forage_db$Vert.invert=="Vertebrate")

```

We have 7 vertebrate predators above 100kg in size.

**1.4 Prey body masses** 

```{r echo=FALSE}

#Adult body masses
#Prey

#Fitted handling times
par(mfrow=c(1,2))
boxplot(forage_db$Prey.mass..mg., ylab="Prey mass (mg)")

dotchart(forage_db$Prey.mass..mg., ylab="Order of the data")

#ggplot(forage_db[forage_db$Vert.invert!="",],aes( Vert.invert,Prey.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
#panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")


```


```{r echo=FALSE, fig.height=7, fig.width=10}

preyBM1<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Angiosperm",],aes( Vert.invert, Prey.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+ggtitle("Grouped:")+theme(axis.title.x=element_blank())

preyBM2<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Protozoan",],aes( Vert.invert, Prey.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

preyBM3<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Invertebrate",],aes( Vert.invert, Prey.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())
                                                                                                                                                                                                                                      
preyBM4<-ggplot(forage_db[forage_db$Vert.invert!="" & forage_db$Vert.invert=="Vertebrate",],aes( Vert.invert, Prey.mass..mg.))+geom_boxplot()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")+theme(axis.title.x=element_blank())

grid.arrange(preyBM1,preyBM2, preyBM3,preyBM4, ncol=2)


#THe largest outliers in vert
#which(forage_db$Predator.mass..mg.>100000000  & forage_db$Vert.invert=="Vertebrate")

```


OUtliers in all covariates except for angiosperms. Zuur et al (2010) recommend transforming covariates; observer or measurement error justify dropping values.

**1.5 Temperature**

```{r echo=FALSE}

par(mfrow=c(1,2))
boxplot(forage_db$Temp..C.., ylab="Temp (c)")

dotchart(forage_db$Temp..C.., ylab="Order of the data")


```

Temperature data looks comparatively outlier-free - yay!

*Note: B.Rosenbaum recommended fitting temperature categorically as likely non-linear.*

2 and 3. Homogeneity of variance and Normality- verified using the residuals produced by the model (in linear regression)-  **TBC**
--

```{r}



```




4. Zeros in the data?
--

Frequency of zeros 

```{r echo=FALSE, fig.height=7, fig.width=10}

fr_h<-ggplot(forage_db, aes(Fittted.h..day.))+geom_histogram(binwidth =1 )+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")

fr_a<-ggplot(forage_db, aes(Fitted.a..median.of.BS.samples.))+geom_histogram()+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+theme_bw(base_size = 13, base_family = "")


grid.arrange(fr_a, fr_h)


r_a<-range(forage_db$Fitted.a..median.of.BS.samples.)
r_h<-range(forage_db$Fittted.h..day.)

which(forage_db$Fittted.h..day.==0)
which(forage_db$Fitted.a..median.of.BS.samples.==0)

```

There are a lot of small values: range for attack rate is `r r_a` and handling time `r r_h`. However, there are no zero responses (unsurprisingly).

5. Collinearity between covariates.
--

Collinearity is defined as existence of correlation between covariates. From reviewing the plot of prey vs predator bodymass (above) we know that these are highly and significantly correlated.

If collinearity is ignored, we may  end with the analysis  where nothing is significant but removing one variable would make others significant (zuur et al. 2010).


```{r echo=FALSE,warning=FALSE, message=FALSE}

#head(forage_db)
pairs(log10(forage_db[,c(24,29,32)]), pcs=19, cex=1, col=forage_db$Vert.invert)

corBM<-cor.test(forage_db$Predator.mass..mg., forage_db$Prey.mass..mg.)

corBM
```

Strangely, correlation value is low - does not look like a right test.

6. Relationships between y and x variables.
---

I've looked at handling time and attack rate with body masses above but have not looked at the temperature yet.


```{r echo=FALSE, fig.height=10, fig.width=10}
a_Temp<-ggplot(forage_db, aes(Temp..C..,log10(Fitted.a..median.of.BS.samples.), col=Vert.invert))+geom_point()

a_Temp<-a_Temp+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+xlab("Temp C")+ylab("Log10 Fitted attack rate median of bootstapped samples")+ggtitle("Fitted attack rate values with Temp")

h_Temp<-ggplot(forage_db, aes(Temp..C..,log10(Fittted.h..day.), col=Vert.invert))+geom_point()

h_Temp<-h_Temp+theme_bw(base_size = 13, base_family = "")+ theme(panel.border = element_blank(),panel.grid.major = element_blank(),
panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"),strip.background = element_rect(colour="white", fill="white"), strip.text.x = element_text(size = 14), legend.position = "bottom", legend.title=element_blank())+xlab("Temp C")+ylab("Log10 Fitted handling times (day)")+ggtitle("Fitted handling times with Temp")

grid.arrange(a_Temp, h_Temp)

```

7. Consider interactions?
---

7.1 Coplot of Prey body mass given Temp on attack rate:

```{r fig.height=7, fig.width=10}

coplot(log10(Fitted.a..median.of.BS.samples.) ~ log10(Prey.mass..mg.)|Temp..C..,data=forage_db, panel = panel.smooth)

```


7.2 Coplot of Prey body mass given Temp on handling time:

```{r fig.height=7, fig.width=10}

coplot(log10(Fittted.h..day.) ~ log10(Prey.mass..mg.)|Temp..C..,data=forage_db,panel = panel.smooth)

```


7.3 Coplot of Predator body mass given Temp on attack rate:

```{r fig.height=7, fig.width=10}

coplot(log10(Fitted.a..median.of.BS.samples.) ~ log10(Predator.mass..mg.)|Temp..C..,data=forage_db,panel = panel.smooth)

```


7.4 Coplot of Predator body mass given Temp on handling time:

```{r fig.height=7, fig.width=10}

coplot(log10(Fittted.h..day.) ~ log10(Predator.mass..mg.)|Temp..C..,data=forage_db,panel = panel.smooth)

```

8. Are observations of the response variable independent?
--

Not sure we need to check this as our response values are fitted. Ask Tim.